---
title: "Taylor Swift"
description: |
  Analysis of Taylor Swift data from TidyTuesday
author: Davina Liu
date: September 28, 2026
format:
  html:
    code-fold: true
    code-summary: "Show code"
    code-tools: true
---

```{r}
library(tidyverse)
```

```{r}
taylor_album_songs <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2023/2023-10-17/taylor_album_songs.csv')
taylor_all_songs <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2023/2023-10-17/taylor_all_songs.csv')
taylor_albums <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2023/2023-10-17/taylor_albums.csv')
```

```{r}
taylor_all_songs |>
    filter(!is.na(album_name), !is.na(duration_ms)) |>
    mutate(minutes = duration_ms / 60000) |>
    ggplot(aes(x = minutes, y = album_name)) +
    geom_boxplot() +
    labs(
    y = "Song length (minutes)",
    title = "Taylor Swift song length by album",
    caption = "Source: TidyTuesday 2023-10-17 (taylor R package)"
  )
```

```{r}
taylor_all_songs |>
  drop_na(album_name, duration_ms) |>
  mutate(minutes = duration_ms / 60000) |>
  group_by(album_name) |>
  summarize(median_min = median(minutes), n_songs = n()) |>
  arrange(median_min)
```

This boxplot shows the distribution of Taylor Swift's song lengths in minutes for each album. Speak Now has the longest median song length of 4.43 minutes, while Taylor Swift Holiday Collection has the shortest median song lengh of 3.27. The biggest outlier is on Red (Taylor's Version), at just over 10 minutes, which is the 10-minute version of "All Too Well.

**Data source:** [TidyTuesday 2023-10-17: Taylor Swift songs](https://github.com/rfordatascience/tidytuesday/tree/main/data/2023/2023-10-17)
**Original source:** Thompson W (2026). *taylor: Lyrics and Song Data for Taylor Swift's Discography.* R package version 4.0.0, <https://taylor.wjakethompson.com>.